---
title: "RSetups Installations"
output:
   rmdformats::robobook:
    self_contained: false
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Install R v4.1.0

Please, download the latest R version based on the system you use.

-   [Download R for Windows](https://cran.r-project.org/bin/windows/base/)

-   [Download R for Linux](https://cran.r-project.org/bin/linux/)

-   [Download R for macOS](https://cran.r-project.org/bin/macosx/)

## 2. Install RStudio (v1.4.1717)

After downloading R, please download RStudio from following link.

-   [Download RStudio](https://www.rstudio.com/products/rstudio/download/#download)

## 3. Install Rtools4 (only for Windows)

For Windows users, you need to install Rtools4 to install packages required in training. 

-   [Download Rtools4](https://cran.r-project.org/bin/windows/Rtools/)

## 4. Install R packages

Open RStudio > Go to R console > Copy/paste following codes.

`install.packages("devtools");`

`devtools::install_github("nm-training/rsetup");`

You may watch video below about how to install R packages:

 <video width="720" height="480" controls>
      <source src="rsetup-install.mp4" type=video/mp4>
    </video>


## 5. Solve R Package Install Path Problem

<iframe width="720" height="480" src="https://www.youtube.com/embed/v5fFNwDCoLE" title="YouTube video player" frameborder="0" allow="accelerometer; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

#### Steps to follow:

1. Search > Advanced System Settings
2. Click Environment Variables
3. Add following based on your system:

```{r eval = F}
Name: R_LIBS_USER

Value: C:\Users\Username\Documents\R\win-library
```


**Note: Set Username same as your actual computer username.**






